Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
review

The impact of a refactoring depends on its complexity, i.e., if the refactoring adds complexity to the codebase it is probably affecting the software maintainability. One evidence of that is the fact of \emph{Cross-Site Scripting} and \emph{Using Components with Know Vulnerabilities} refactorings endure more cases without any impact in the maintainability. Typically, these type of vulnerabilities are one line fixes --- adding an \texttt{escape} function or changing the version of the component, respectively. Whereas, Broken Authentication and vulnerabilities such as the one presented in Section~\ref{sec:motivation} responsible by DoS attacks are more difficult to fix (several code lines deleted and added). Another example is the Apple authentication flaw discovered in 2017 (CVE-2017-13872)\footnote{CVE-2017-13872 details available at https://support.apple.com/en-us/HT208315 (Accessed on \today{})}, where any user could login as root with an empty password. Patrick Wardle examined the cause of the issue\footnote{\emph{Why $<$blank$>$ Gets You Root} available at https://objective-see.com/blog/blog\_0x24.html (Accessed on \today{})} and conclude that the flaw was due to the introduction of high cyclomatic complexity in a method used to verify the password. In sum, \emph{Cross-Site Scripting} and \emph{Using Components with Known Vulnerabilities} should take part of the developers preocupations along with the other patterns that explicitly hinder maintainability because despite their low complexity these are patterns that still produce a considerable negative impact on the maintainability. Real efforts have been made in creating and incorporating coding standards and best practices in software production. However, security is still far from perfection and fixing vulnerabilities might hinder software maintainability. Thus, it is important to provide tool support to developers to help them applying these patterns without harming software maintainability.

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to validity of this study.
%
\subsection{Construct}
%
The maintainability formula was inferred based on the reports of the Better Code Hub.
The high amount of different projects and backgrounds may require different maintainablity
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table~\ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

>>>>

The impact of a refactoring depends on its complexity, i.e., if the refactoring
adds complexity to the codebase it is probably affecting the software
maintainability. One evidence of that is the fact of \emph{Cross-Site
Scripting} and \emph{Using Components with Know Vulnerabilities} refactorings
endure more cases without any impact in the maintainability. Typically, these
type of vulnerabilities are one line fixes --- adding an \texttt{escape}
function or changing the version of the component, respectively. Whereas,
Broken Authentication and vulnerabilities such as the one presented in
Section~\ref{sec:motivation} responsible by DoS attacks are more difficult to
fix (several code lines deleted and added). Another example is the Apple
authentication flaw discovered in 2017 (CVE-2017-13872)\footnote{CVE-2017-13872
details available at https://support.apple.com/en-us/HT208315 (Accessed on
\today{})}, where any user could login as root with an empty password. Patrick
Wardle examined the cause of the issue\footnote{\emph{Why $<$blank$>$ Gets You
Root} available at https://objective-see.com/blog/blog\_0x24.html (Accessed on
\today{})} and conclude that the flaw was due to the introduction of high
cyclomatic complexity in a method used to verify the password. In sum,
\emph{Cross-Site Scripting} and \emph{Using Components with Known
Vulnerabilities} should take part of the developers preoccupations along with
the other patterns that explicitly hinder maintainability because despite their
low complexity these are patterns that still produce a considerable negative
impact on the maintainability. Real efforts have been made in creating and
incorporating coding standards and best practices in software production.
However, security is still far from perfection and fixing vulnerabilities might
hinder software maintainability. Thus, it is important to provide tool support
to developers to help them applying these patterns without harming software
maintainability.

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to validity of this study.
%
\subsection{Construct}
%

\Luis{Better Code Hub -> BCH}
The maintainability formula was inferred based on the reports of the Better Code Hub.
The high amount of different projects and backgrounds may require different maintainability
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table~\ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

\luis{many directions such as -> many directions:}
\luis{evaluate the impact of programming languages of the
maintainability of each refactoring pattern; - > evaluate the impact of each refactoring pattern on the maintainbility of each  }
